### 2016-10-08 oldmort.Rnw
fix errors for cause 41

<<causes41>>=
load("data/vb.rda")
x <- substr(vb$ULORSAK, 1, 2)
vb$event <- vb$event & (!is.na(vb$ULORSAK)) & (x %in% "41")
vb$exposure <- with(vb, exit - enter)
vbTab <- aggregate(vb[, c("event", "exposure")], 
                   vb[, c("sex", "age", "period", "cohort", 
                          "urban", "civst", "hisclass")], 
                   FUN = sum)
vbTab$hisclass <- factor(vbTab$hisclass)
vbTab$age <- factor(vbTab$age)
@

@@

@@

<<41hazplotm, fig.cap = cap1m, fig.scap = scap1m, fig.height = 7>>=
plotHaz.glm(resm[-(1:6)], main = labb, col = scol, layout = c(2, 2))
@

@@

<<41cumslogw, fig.cap = cap12log, fig.scap = scap12log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw[-(1:6)], col = scol, logScale = FALSE, ylab = "H(65|40)",
main = "Women")
mloutp <- plotED.glm(resm[-(1:6)], col = scol, logScale = FALSE, ylab = "H(65|40)",
main = "Men")
par(oldpar)
@

@@

<<41hazplotwold, fig.cap = cap2w, fig.scap = scap2w, fig.height = 7>>=
##source("R/plotHaz.R")
plotHaz.glm(resw[-(1:6)], main = labb, layout = c(2, 2), col = scol)
@

<<41hazplotmold, fig.cap = cap2w, fig.scap = scap2m, fig.height = 7>>=
plotHaz.glm(resm[-(1:6)], main = labb, layout = c(2, 2), col = scol)
@

@@

<<41cumslogwm, fig.cap = cap22log, fig.scap = scap22log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw[-(1:6)], col = scol, logScale = FALSE, ylab = "H(90|65)",
main = "Women")
mloutp <- plotED.glm(resm[-(1:6)], col = scol, logScale = FALSE, ylab = "H(90|65)",
main = "Men")
par(oldpar)
@

>>>>

<<causes41>>=
load("data/vb.rda")
vb <- cal.window(vb, c(1961, 2001))
x <- substr(vb$ULORSAK, 1, 2)
vb$event <- vb$event & (!is.na(vb$ULORSAK)) & (x %in% "41")
vb$exposure <- with(vb, exit - enter)
vb$cohort <- factor(vb$cohort)
vb$period <- factor(vb$period)
vbTab <- aggregate(vb[, c("event", "exposure")], 
                   vb[, c("sex", "age", "period", "cohort", 
                          "urban", "civst", "hisclass")], 
                   FUN = sum)
vbTab$hisclass <- factor(vbTab$hisclass)
vbTab$age <- factor(vbTab$age)
@

@@

Models are fitted separately for each ten-year time period, from  1961 to
2000. We stratify on HISCLASS
and use the covariates {\tt sex}, {\tt   civst}, and {\tt urban}
(Skellefteå town or outside). The cumulative
hazards at the end of the time period (60 if 40--64, 90 if 65--89) are the
main target in our analysis: These numbers are used in the process of
graphically illustrating the development over time.

@@

plotHaz.glm(resw, main = labb, col = scol, layout = c(2, 2))
@

<<41hazplotm, fig.cap = cap1m, fig.scap = scap1m, fig.height = 7>>=
plotHaz.glm(resm, main = labb, col = scol, layout = c(2, 2))
@

@@

<<41cumslogw, fig.cap = cap12log, fig.scap = scap12log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "H(65|40)",
main = "Women")
mloutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "H(65|40)",
main = "Men")
par(oldpar)
@

@@

<<41hazplotwold, fig.cap = cap2w, fig.scap = scap2w, fig.height = 7>>=
##source("R/plotHaz.R")
plotHaz.glm(resw, main = labb, layout = c(2, 2), col = scol)
@

<<41hazplotmold, fig.cap = cap2w, fig.scap = scap2m, fig.height = 7>>=
plotHaz.glm(resm, main = labb, layout = c(2, 2), col = scol)
@

@@

<<41cumslogwm, fig.cap = cap22log, fig.scap = scap22log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "H(90|65)",
main = "Women")
mloutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "H(90|65)",
main = "Men")
par(oldpar)
@
